Paper Figure Generation

### 2022-08-26 R/5'CutSiteAnalysisDataGeneration.rmd
Read length merging in plotting
- Changed nucleotide frequency and sequence frequency plotting to recognize data with merged read lengths and not stratify along a secondary y-axis.
- Created function for making read-length-merged nucleotide frequency and sequence frequency data anchored to mismatches. (This was a bad idea... data anchored to a mismatch causes variable cut-site positions that when combined destroy any relevant signals.)
- Updated 5' general read sequence analysis to perform nucleotide frequency generation and optionally combine read lengths.
- Updated paper figure generation.

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteAnalysis = function(lesion, repetition, timepoint, cellType, directory,
                           queryPattern, sequencesName, readMinMax,
                           dataTypeString = dataTypeStrings$alignedReads, fileExtension = ".bed") {
  readData = fread(generateFilePath(
    directory, dataTypeString, fileExtension,
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repetition, expansionNum = expansionOffset, filtering = filtering
  ))
  readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
  readData = readData[Read_Length >= readMinMax[1] & Read_Length <= readMinMax[2]]

  seqFreq = getSequenceFreqByReadLengthAndPos(readData, queryPattern = queryPattern, posType = FIVE_PRIME)
  seqFreq[, Position := Position - 10]
  fwrite(seqFreq, sep = '\t', file = generateFilePath(
      directory = directory, dataTypeStrings$sequenceFrequency, ".tsv",
      cellType = cellType, lesion = lesion, repitition = repetition,
      timepoint = timepoint, sequence = sequencesName, filtering = filtering))
}
```

@@

cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax)
cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax)
cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", yeastReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", arabidopsisReadMinMax)
cutSiteAnalysis("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", EColiReadMinMax)
```

>>>>

```{r define_all_that_and_a_bag_of_chips_function}
cutSiteAnalysis = function(lesion, repetition, timepoint, cellType, directory,
                           queryPattern, sequencesName, readMinMax,
                           alsoComputeCombinedReadLengths = FALSE, alsoComputeNucFreq = FALSE) {
  readData = fread(generateFilePath(
    directory, dataTypeStrings$alignedReads , ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repetition, expansionNum = expansionOffset, filtering = filtering
  ))
  readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
  readData = readData[Read_Length >= readMinMax[1] & Read_Length <= readMinMax[2]]

  seqFreq = getSequenceFreqByReadLengthAndPos(readData, queryPattern = queryPattern, posType = FIVE_PRIME)
  seqFreq[, Position := Position - 10]

  fwrite(seqFreq, sep = '\t', file = generateFilePath(
    directory = directory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = cellType, lesion = lesion, repitition = repetition,
    timepoint = timepoint, sequence = sequencesName, filtering = filtering))

  if (alsoComputeNucFreq) {

    nucFreq = tabulateNucFreqByPosTimepointAndLength(setNames(list(readData),timepoint), FIVE_PRIME)
    nucFreq[, Position := Position - 10]

    fwrite(nucFreq, sep = '\t', file = generateFilePath(
      directory = directory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
      cellType = cellType, lesion = lesion, repitition = repetition,
      timepoint = timepoint, filtering = filtering))

  }

  if (alsoComputeCombinedReadLengths) {
    readData[, Read_Length := NULL]
    readData[, Read_Length := "combined"]

    seqFreq = getSequenceFreqByReadLengthAndPos(readData, queryPattern = queryPattern, posType = FIVE_PRIME)
    seqFreq[, Position := Position - 10]

    fwrite(seqFreq, sep = '\t', file = generateFilePath(
        directory = directory, dataTypeStrings$sequenceFrequency, ".tsv",
        cellType = cellType, lesion = lesion, repitition = repetition,
        timepoint = timepoint, sequence = sequencesName, filtering = filtering,
        additionalInformation = "combined_read_lengths"))

    if (alsoComputeNucFreq) {

      nucFreq = tabulateNucFreqByPosTimepointAndLength(setNames(list(readData),timepoint), FIVE_PRIME)
      nucFreq[, Position := Position - 10]

      fwrite(nucFreq, sep = '\t', file = generateFilePath(
        directory = directory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
        cellType = cellType, lesion = lesion, repitition = repetition,
        timepoint = timepoint, filtering = filtering, additionalInformation = "combined_read_lengths"))

  }

  }
}
```

@@

cutSiteAnalysis("CPD", "all_reps", "1h", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE,
                alsoComputeNucFreq = TRUE)
cutSiteAnalysis("6-4", "all_reps", "20min", "NHF1", NHF1GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombineReadLengths = TRUE)
cutSiteAnalysis("cisplatin", "rep1", "90min", "GM12878", GM12878GeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", humanReadMinMax, alsoComputeCombinedReadLengths = TRUE)
cutSiteAnalysis("CPD", "all_reps", "20min", "yeast", yeastGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", yeastReadMinMax, alsoComputeCombinedReadLengths = TRUE)
cutSiteAnalysis("CPD", "all_reps", "ZT2", "Arabidopsis", arabidopsisGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", arabidopsisReadMinMax, alsoComputeCombinedReadLengths = TRUE)
cutSiteAnalysis("CPD", "all_reps", "5min", "E_coli_WT", EColiGeneralReadSequenceDataDirectory,
                HYVPattern, "HYV", EColiReadMinMax, alsoComputeCombinedReadLengths = TRUE)
```

### 2022-08-26 R/PaperFigureGeneration.rmd
Read length merging in plotting
- Changed nucleotide frequency and sequence frequency plotting to recognize data with merged read lengths and not stratify along a secondary y-axis.
- Created function for making read-length-merged nucleotide frequency and sequence frequency data anchored to mismatches. (This was a bad idea... data anchored to a mismatch causes variable cut-site positions that when combined destroy any relevant signals.)
- Updated 5' general read sequence analysis to perform nucleotide frequency generation and optionally combine read lengths.
- Updated paper figure generation.

```{r read_figure_4_data}
NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))
NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
  ))
}
NHF1GeneralReadsCPDSeqFreqAllReps1hFiltered = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "NHF1", lesion = "CPD", timepoint = "1h",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2Filtered = fread(generateFilePath(
  arabidopsisGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
yeastGeneralReadsCPDSeqFreqAllReps20MinFiltered = fread(generateFilePath(
  yeastGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "yeast", lesion = "CPD", timepoint = "20min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
EColiGeneralReadsCPDSeqFreqAllReps5MinFiltered = fread(generateFilePath(
  EColiGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "E_coli_WT", lesion = "CPD", timepoint = "5min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
```

@@

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4C, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(NHF1GeneralReadsCPDSeqFreqAllReps1hFiltered[Position <= 7],
                        title = "NHF1 CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8))
```
```{r figure_4D, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2Filtered[Position <= 7],
                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 24, maxReadLength = 30, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8))
```
```{r figure_4E, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(yeastGeneralReadsCPDSeqFreqAllReps20MinFiltered[Position <= 7],
                        title = "Yeast CPD 20min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 22, maxReadLength = 25, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8))
```
```{r figure_4F, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFiltered[Position <= 7],
                        title = "E. coli CPD 5min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, minReadLength = 11, maxReadLength = 13, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8))
```

@@

NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", includedMismatches = "CC>TT",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
  ))
}

@@

```{r figure_6A, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative C>T Frequency")

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative C>T Frequency")
```
```{r figure_6B, fig.width = 5, fig.height = 5}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored HYV Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
                        xAxisOffset = 1)

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered CC>TT 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
```
```{r figure_6C, fig.width = 7.5, fig.height = 5}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

@@

```{r read_figure_S4_data}
NHF1GeneralReadsSixFourSeqFreqAllReps20minFiltered = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "NHF1", lesion = "6-4", timepoint = "20min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered"
))
GM12878GeneralReadsCisplatinSeqFreqRep1_90minFiltered = fread(generateFilePath(
  GM12878GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "GM12878", lesion = "cisplatin", timepoint = "90min",
  repitition = "rep1", sequence = "HYV", filtering = "TGG_filtered"
))
```

```{r figure_S4, fig.width = 5, fig.height = 6}
plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFiltered[Position <= 7],
                        title = "NHF1 6-4 20min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisOffset = 1)
plotSequenceFrequencies(GM12878GeneralReadsCisplatinSeqFreqRep1_90minFiltered[Position <= 7],
                        title = "GM12878 cisplatin 90min Rep1 TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisOffset = 1)
```

@@

```{r figure_S5, fig.width = 9, fig.height = 5}
plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
                                         title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative GG>AA Frequency")
```

>>>>

```{r read_figure_4_data}
NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))
NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered"
  ))
}

NHF1GeneralReadsCPDNucFreqAllReps1hFilteredCombined = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps", timepoint = "1h",
  filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
))
NHF1GeneralReadsCPDSeqFreqAllReps1hFilteredCombined = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "NHF1", lesion = "CPD", timepoint = "1h", repitition = "all_reps",
  sequence = "HYV", filtering = "TGG_filtered", additionalInformation = "combined_read_lengths"
))
arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2FilteredCombined = fread(generateFilePath(
  arabidopsisGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "Arabidopsis", lesion = "CPD", timepoint = "ZT2",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
  additionalInformation = "combined_read_lengths"
))
yeastGeneralReadsCPDSeqFreqAllReps20MinFilteredCombined = fread(generateFilePath(
  yeastGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "yeast", lesion = "CPD", timepoint = "20min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
  additionalInformation = "combined_read_lengths"
))
EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined = fread(generateFilePath(
  EColiGeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "E_coli_WT", lesion = "CPD", timepoint = "5min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
  additionalInformation = "combined_read_lengths"
))
```

@@

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 8,
#                         endBasedCheckPositions = -10, displayPValue = TRUE, xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4C, fig.width = 6.5, fig.height = 4.75}
plotNucFreqVsReadLengthBarPlot(NHF1GeneralReadsCPDNucFreqAllReps1hFilteredCombined[Position <= 7], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered Nuc Freq",
                               secondaryYAxisLabel = "Read Length", ylim = c(0,1),
                               posType = FIVE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10,
                               xAxisLabel = "Mismatch Relative Position")
```
```{r figure_4D, fig.width = 5, fig.height = 4}
plotSequenceFrequencies(NHF1GeneralReadsCPDSeqFreqAllReps1hFilteredCombined[Position <= 7],
                        title = "NHF1 CPD 1h All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
```
```{r figure_4E, fig.width = 5, fig.height = 4}
plotSequenceFrequencies(arabidopsisGeneralReadsCPDSeqFreqAllRepsZT2FilteredCombined[Position <= 7],
                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
```
```{r figure_4F, fig.width = 5, fig.height = 4}
plotSequenceFrequencies(yeastGeneralReadsCPDSeqFreqAllReps20MinFilteredCombined[Position <= 7],
                        title = "Yeast CPD 20min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
```
```{r figure_4G, fig.width = 5, fig.height = 4}
plotSequenceFrequencies(EColiGeneralReadsCPDSeqFreqAllReps5MinFilteredCombined[Position <= 7],
                        title = "E. coli CPD 5min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisOffset = 1,
                        expansionOffset = 10, xAxisLabel = "5' Relative Position",
                        xAxisBreaks = c(-8, 0, 8), ylimMax = 0.6, ylimMaxModifier = 1)
```

@@

NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv", timepoint = "1h",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", includedMismatches = "CC>TT",
    strandPolarity = "three_prime", anchored = TRUE, sequence = "HYV", filtering = "TGG_filtered",
))

@@

```{r figure_6A, fig.width = 5, fig.height = 5.5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative CC>TT Frequency")

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative CC>TT Frequency")
```
```{r figure_6B, fig.width = 5, fig.height = 5}
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored HYV Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
                        xAxisOffset = 1)
```
```{r figure_6C, fig.width = 7.5, fig.height = 5}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

@@

```{r read_figure_S4_data}
NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined = fread(generateFilePath(
  NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "NHF1", lesion = "6-4", timepoint = "20min",
  repitition = "all_reps", sequence = "HYV", filtering = "TGG_filtered",
  additionalInformation = "combined_read_lengths"
))
GM12878GeneralReadsCisplatinSeqFreqRep1_90minFilteredCombined = fread(generateFilePath(
  GM12878GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
  cellType = "GM12878", lesion = "cisplatin", timepoint = "90min",
  repitition = "rep1", sequence = "HYV", filtering = "TGG_filtered",
  additionalInformation = "combined_read_lengths"
))
```

```{r figure_S4, fig.width = 5, fig.height = 4}
plotSequenceFrequencies(NHF1GeneralReadsSixFourSeqFreqAllReps20minFilteredCombined[Position <= 7],
                        title = "NHF1 6-4 20min All Reps TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisOffset = 1, ylimMax = 0.6, ylimMaxModifier = 1)
plotSequenceFrequencies(GM12878GeneralReadsCisplatinSeqFreqRep1_90minFilteredCombined[Position <= 7],
                        title = "GM12878 cisplatin 90min Rep1 TGG-Filtered General Reads HYV Freq",
                        secondaryYAxisLabel = "Read Length", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"), xAxisBreaks = c(-8, 0, 8),
                        expansionOffset = 10, minReadLength = 23, maxReadLength = 29, backgroundPositions = -9:-4,
                        checkPositions = -1, displayPValue = FALSE, xAxisLabel = "5' Relative Position",
                        xAxisOffset = 1, ylimMax = 0.6, ylimMaxModifier = 1)
```

@@

```{r figure_S5, fig.width = 5, fig.height = 5.5}
plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative GG>AA Frequency")
```
